Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-08-15 Paper/main.tex

\begin{table}[H]
\caption{Determinants of updating}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use the following statistic to measure updating: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says.
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}

@@

\begin{table}[H]
    \caption{Direct Updating}
    \begin{subtable}{.5\linewidth}
      \centering
        \caption{Pilot}
        \scriptsize{\input{./Tables/update_beleif_1.tex}}
    \end{subtable}%
    \begin{subtable}{.5\linewidth}
      \centering
        \caption{Scale Up}
        \scriptsize{\input{./Tables/update_beleif_2.tex}}
    \end{subtable} 
           \footnotesize    
  \textit{Notes:} 
    Summary statistics of parties' update in beliefs; measured as $\frac{exit-initial}{initial}$, for both \emph{Pilot} and \emph{Scale Up}.
    \textit{Do file: } \texttt{update\_beleif\_ss.do}
\end{table}

@@

%#appendix 
\begin{table}[H]
    \caption{Correlation conciliation vs overconfidence}
    \label{Table_concvsoc}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    All measures of OC are relative. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{corr\_con\_oc.do corr\_con\_oc\_B.do}
\end{table}

\begin{table}[H]
    \caption{Correlation conciliation vs overconfidence}
    \label{Table_concvsoc_theta}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc_theta.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   We use the following statistic to measure overconfidence: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won.. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{con\_vs\_oc\_theta.do}
\end{table}

>>>>

\begin{table}[H]
\caption{Determinants of updating (Theta)}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . Theta updating refers to the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. 
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}

\begin{table}[H]
\caption{Determinants of updating (Relative)}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_rel.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated. Relative updating is computed as $\frac{exitsurvey-initialsurvey}{initialsurvey}$.
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}
\end{landscape}

@@

\begin{table}[H]
    \caption{Direct Updating}
     \begin{center}
       \scriptsize{\input{./Tables/direct_updating.tex}}
    \end{center}
           \footnotesize    
  \textit{Notes:} 
    Summary statistics of parties' update in beliefs; measured as $\frac{exit-initial}{initial}$, for both \emph{Pilot} and \emph{Scale Up}. Note that Scale Up is not divided by treatment. 
    \textit{Do file: } \texttt{update\_beleif\_ss.do}
\end{table}

@@

%#appendix 
\begin{table}[H]
    \caption{Correlation conciliation vs overconfidence - Pilot data}
    \label{Table_concvsoc}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    All measures of OC are relative. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{corr\_con\_oc.do corr\_con\_oc\_B.do}
\end{table}

\begin{table}[H]
    \caption{Correlation conciliation vs update - Pilot data}
    \label{Table_concvsoc_theta}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc_theta.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   We use the following statistic to measure updating: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won.. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{con\_vs\_oc\_theta.do}
\end{table}
